A First Effort for a Distributed Segment-based Approach on Topology-agnostic Self-Assembled Nano Networks

### 2013-09-17 trunk/PAPER/paper.tex
- minor updates

\title{A Distributed Segment-based Approach for Topology-agnostic
Routing in Self-Assembled Nano Networks}

\author{Vincenzo~Catania, Salvatore Monteleone~and~Davide~Patti% 
\thanks{The authors are with the Dipartimento di Ingegneria
Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
(email: \{vcatania,dpatti\}@dieei.unict.it).}}

@@

\begin{abstract}
In this paper we present DiSR, a first effort for a distributed
segment-based approach to routing in a nano-scale, topology agnostic
scenario based on DNA self-assembly. The main aim is exploiting the
already-proven qualities of segment-based routing without neither requiring a
topology graph as input, nor needing a centralized algorithm to
configure network paths. 
After introducing the conceptual elements and the execution model of
DiSR, we developed the opensource Nanoxim tool to show how the proposed
approach can be used to discover irregular network topology while
estabilishing network segments. Finally, we perfomed some quantitive
comparisons to demonstrate how DiSR compares against classic
segment-based algorithm and other broadcasting based approaches.  The
results shows how DiSR still preserves some important features
(connectivity, defect tolerance, scalability)  while avoiding centralized
tree-based broadcasting and resource hungry solutions such as virtual
channels and hardware redundancy.
\end{abstract}

>>>>

\title{A First Effort for a Distributed Segment-based Approach on Topology-agnostic
Self-Assembled Nano Networks}

\author{Vincenzo~Catania, Andrea Mineo, Salvatore Monteleone~and~Davide~Patti% 
\thanks{The authors are with the Dipartimento di Ingegneria
Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
(email: \{vincenzo.catania,amineo,salvatore.monteleone,davide.patti\}@dieei.unict.it).}}

@@

\begin{abstract}
In this paper we present DiSR, a first effort for a distributed
segment-based approach to routing and defect mapping in a nano-scale, topology agnostic
scenario based on DNA self-assembly. The main aim is exploiting the
already-proven qualities of segment-based routing without neither requiring a
topology graph as input, nor needing a centralized algorithm to
configure network paths. 
After introducing the conceptual elements and the execution model of
DiSR, we developed the opensource Nanoxim tool to show how the proposed
approach can be used to discover irregular network topology while
estabilishing network segments.  The results shows how DiSR still
preserves some important features
(connectivity, defect tolerance, scalability)  while avoiding centralized
tree-based broadcasting and resource hungry solutions such as virtual
channels and hardware redundancy. Finally, we analyzed a possible
VHDL hardware implementation of the required control logic and storage for
DiSR, demonstrating a relatively acceptable impact ranging from 15 to
about 25\% of the budget of transistors available for each node.
\end{abstract}
